Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)

### 2025-09-22 README.qmd

```{=html}
<!--
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/archyjobads/main?urlpath=rstudio) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.15847809.svg)](https://doi.org/10.5281/zenodo.15847809)
-->
```

@@

> Ye Zhi, Ben Marwick, Li Hao, Shuwen Pei (2025). Spherical harmonic
> analysis of faceted spheroids identifies shaping strategies and
> standardisation at Qianshangying (North China)". Submitted to *Journal
> of Archaeological Science*

A pre-print of this paper is freely available on SocArXiv:
https://osf.io/preprints/socarxiv/

>>>>

```{=html}
<!--
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/archyjobads/main?urlpath=rstudio) 
-->
```

@@

> Ye Zhi, Ben Marwick, Li Hao, Shuwen Pei (2025). Spherical harmonic
> analysis of faceted spheroids identifies shaping strategies and
> standardisation at Qianshangying (North China). Submitted to *Journal
> of Archaeological Science*

A pre-print of this paper is freely available on SocArXiv:
https://osf.io/preprints/socarxiv/ The data and code are archived at OSF:  https://doi.org/10.17605/OSF.IO/CTNE9/

### 2025-09-22 analysis/paper/paper.qmd

We generated 3D models of the cores for morphometric and technological analysis. Digital data were captured using Artec Spider, and post-processing was carried out with Artec Studio 18. The 3D scan files and all the R and Python code used in the analyses reported here are openly available online at https://osf.io/ctne9/.

@@

The 3d models from QSY site used in this study are openly available at https://osf.io/ctne9/?view_only=eb93ea8a29bb4b40a407f7eba39c6fc1

>>>>

We generated 3D models of the cores for morphometric and technological analysis. Digital data were captured using Artec Spider, and post-processing was carried out with Artec Studio 18. The 3D scan files and all the R and Python code used in the analyses reported here are openly available online at https://doi.org/10.17605/OSF.IO/CTNE9/

@@

The 3d models from QSY site used in this study are openly available at https://doi.org/10.17605/OSF.IO/CTNE9
